Ground state energy of quantum dots using the coupled cluster method

### 2018-06-06 project_2/article/article.tex
Fix merge conflict

    \begin{table}
        \centering
        \caption{N = 2}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\ \hline
                         &  $1$  & $0.596333$ & $0.596333$ & $0.596333$ \\
                         &  $2$  & $0.596333$ & $0.512520$ & $0.512520$ \\
                         &  $3$  & $0.526903$ & $0.505972$ & $0.442235$ \\
                         &  $4$  & $0.526903$ & $0.499216$ & $0.442011$ \\
                         &  $5$  & $0.525666$ & $0.497172$ & $0.443293$ \\
  \multirow{2}{*}{$0.1$} &  $6$  & $0.525666$ & $0.494232$ & $0.443145$ \\
                         &  $7$  & $0.525635$ & $0.493142$ & $0.443056$ \\
                         &  $8$  & $0.525635$ & $0.491895$ & $0.442981$ \\
                         &  $9$  & $0.525635$ & $0.491262$ & $0.491262$ \\
                         &  $10$ & $0.525635$ & $0.490649$ & $0.442886$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $1$  & $1.886227$ & $1.886227$ & $1.886227$ \\
                         &  $2$  & $1.886227$ & $1.786914$ & $1.786914$ \\
                         &  $3$  & $1.799856$ & $1.778903$ & $1.681979$ \\
                         &  $4$  & $1.799856$ & $1.760117$ & $1.673881$ \\
                         &  $5$  & $1.799748$ & $1.754385$ & $1.670053$ \\
  \multirow{2}{*}{$0.5$} &  $6$  & $1.799748$ & $1.748232$ & $1.667804$ \\
                         &  $7$  & $1.799745$ & $1.745231$ & $1.666474$ \\
                         &  $8$  & $1.799745$ & $1.742548$ & $1.665494$ \\
                         &  $9$  & $1.799743$ & $1.740860$ & $1.664805$ \\
                         &  $10$ & $1.799743$ & $1.739444$ & $1.664270$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $1$  & $3.253314$ & $3.253314$ & $3.253314$ \\
                         &  $2$  & $3.253314$ & $3.152328$ & $3.152328$ \\
                         &  $3$  & $3.162691$ & $3.141827$ & $3.039048$ \\
                         &  $4$  & $3.162691$ & $3.118679$ & $3.025273$ \\
                         &  $5$  & $3.161921$ & $3.110967$ & $3.017944$ \\
  \multirow{2}{*}{$1.0$} &  $6$  & $3.161921$ & $3.103338$ & $3.013923$ \\
                         &  $7$  & $3.161909$ & $3.099324$ & $3.011405$ \\
                         &  $8$  & $3.161909$ & $3.095916$ & $3.009621$ \\
                         &  $9$  & $3.161909$ & $3.093662$ & $3.008343$ \\
                         &  $10$ & $3.161909$ & $3.091818$ & $3.007357$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $1$  & $5.772454$ & $5.772454$ & $5.772454$ \\
                         &  $2$  & $5.772454$ & $5.671234$ & $5.671234$ \\
                         &  $3$  & $5.679048$ & $5.658272$ & $5.553528$ \\
                         &  $4$  & $5.679048$ & $5.631669$ & $5.534333$ \\
                         &  $5$  & $5.677282$ & $5.622092$ & $5.523490$ \\
  \multirow{2}{*}{$2.0$} &  $6$  & $5.677282$ & $5.613118$ & $5.517552$ \\
                         &  $7$  & $5.677206$ & $5.608130$ & $5.513709$ \\
                         &  $8$  & $5.677206$ & $5.604026$ & $5.511012$ \\
                         &  $9$  & $5.677204$ & $5.601216$ & $5.509050$ \\
                         &  $10$ & $5.677204$ & $5.598946$ & $5.507540$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}
    \end{table}

    \begin{table}
        \centering
        \caption{N = 6}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\ \hline
                         &  $1$  & \nan & \nan & \nan \\
                         &  $2$  & $4.864244$ & $4.864244$ & $4.864244$ \\
                         &  $3$  & $4.435740$ & \nan & $4.319901$ \\
                         &  $4$  & $4.019787$ & \nan & $3.829962$ \\
                         &  $5$  & $3.963149$ & \nan & $3.666722$ \\
  \multirow{2}{*}{$0.1$} &  $6$  & $3.870617$ & \nan & $3.597876$ \\
                         &  $7$  & $3.863135$ & \nan & $3.590388$ \\
                         &  $8$  & $3.852880$ & \nan & $3.587711$ \\
                         &  $9$  & $3.852591$ & \nan & $3.587291$ \\
                         &  $10$ & $3.852393$ & \nan & $3.587136$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $1$  & \nan & \nan & \nan \\
                         &  $2$  & $13.640713$ & $13.640713$ & $13.640713$ \\
                         &  $3$  & $13.051620$ & $13.385987$ & $12.901520$ \\
                         &  $4$  & $12.357471$ & $13.261097$ & $12.057345$ \\
                         &  $5$  & $12.325128$ & $13.138572$ & $11.934988$ \\
  \multirow{2}{*}{$0.5$} &  $6$  & $12.271499$ & $13.084158$ & $11.864098$ \\
                         &  $7$  & $12.271375$ & $13.068399$ & $11.849762$ \\
                         &  $8$  & $12.271361$ & $13.055561$ & $11.841330$ \\
                         &  $9$  & $12.271337$ & $13.045386$ & $11.835470$ \\
                         &  $10$ & $12.271326$ & $13.037878$ & $11.831351$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $1$  & \nan & \nan & \nan \\
                         &  $2$  & $22.219813$ & $22.219813$ & $22.219813$ \\
                         &  $3$  & $21.593198$ & $21.974675$ & $21.423811$ \\
                         &  $4$  & $20.766919$ & $21.854191$ & $20.429265$ \\
                         &  $5$  & $20.748402$ & $21.793624$ & $20.332454$ \\
  \multirow{2}{*}{$1.0$} &  $6$  & $20.720257$ & $21.750091$ & $20.274013$ \\
                         &  $7$  & $20.720132$ & $21.718843$ & $20.249849$ \\
                         &  $8$  & $20.719248$ & $21.695224$ & $20.234705$ \\
                         &  $9$  & $20.719248$ & $21.675931$ & $20.224389$ \\
                         &  $10$ & $20.719217$ & $21.661830$ & $20.21707530$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $1$  & \nan & \nan & \nan \\
                         &  $2$  & $37.281425$ & $37.281425$ & $37.281425$ \\
                         &  $3$  & $36.637217$ & $37.042127$ & $36.450634$ \\
                         &  $4$  & $35.689555$ & $36.925664$ & $35.328432$ \\
                         &  $5$  & $35.681729$ & $36.864367$ & $35.250185$ \\
  \multirow{2}{*}{$2.0$} &  $6$  & $35.672333$ & $36.812895$ & $35.200308$ \\
                         &  $7$  & $35.671851$ & $36.775986$ & $35.168245$ \\
                         &  $8$  & $35.670358$ & $36.747864$ & $35.147097$ \\
                         &  $9$  & $35.670333$ & $36.725261$ & $35.131953$ \\
                         &  $10$ & $35.670144$ & $36.708362$ & $35.121033$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\

>>>>

    \subsection{Ground state energies for two-dimensional quantum dots}
        Here we show the ground state energies for the two-dimensional quantum
        dots using restriced Hartree-Fock (RHF), coupled cluster doubles using
        both the harmonic oscillator basis and the Hartree-Fock basis which we
        construct after running the RHF-method. We have chosen the convergence
        criteria to be $\num{1e-6}$ in our results for the sake of comparison
        with M. P. Lohne\cite{lohne2011ab}.

    \begin{table}
        \centering
        \caption{N = 2}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\
                \hline
                           &  $1$  & $0.596333$ & $0.596333$ & $0.596333$ \\
                           &  $2$  & $0.596333$ & $0.512520$ & $0.512520$ \\
                           &  $3$  & $0.526903$ & $0.505972$ & $0.442235$ \\
                           &  $4$  & $0.526903$ & $0.499216$ & $0.442011$ \\
                           &  $5$  & $0.525666$ & $0.497172$ & $0.443293$ \\
    \multirow{2}{*}{$0.1$} &  $6$  & $0.525666$ & $0.494232$ & $0.443145$ \\
                           &  $7$  & $0.525635$ & $0.493142$ & $0.443056$ \\
                           &  $8$  & $0.525635$ & $0.491895$ & $0.442981$ \\
                           &  $9$  & $0.525635$ & $0.491262$ & $0.442927$ \\
                           &  $10$ & $0.525635$ & $0.490649$ & $0.442886$ \\
                           &  $11$ & $0.525635$ & $0.490262$ & $0.442853$ \\
                           &  $12$ & $0.525635$ & $0.489918$ & $0.442827$ \\
                \hline

                           &  $1$  & $1.886227$ & $1.886227$ & $1.886227$ \\
                           &  $2$  & $1.886227$ & $1.786914$ & $1.786914$ \\
                           &  $3$  & $1.799856$ & $1.778903$ & $1.681979$ \\
                           &  $4$  & $1.799856$ & $1.760117$ & $1.673881$ \\
                           &  $5$  & $1.799748$ & $1.754385$ & $1.670053$ \\
    \multirow{2}{*}{$0.5$} &  $6$  & $1.799748$ & $1.748232$ & $1.667804$ \\
                           &  $7$  & $1.799745$ & $1.745231$ & $1.666474$ \\
                           &  $8$  & $1.799745$ & $1.742548$ & $1.665494$ \\
                           &  $9$  & $1.799743$ & $1.740860$ & $1.664805$ \\
                           &  $10$ & $1.799743$ & $1.739444$ & $1.664270$ \\
                           &  $11$ & $1.799742$ & $1.738416$ & $1.663856$ \\
                           &  $12$ & $1.799742$ & $1.737562$ & $1.663522$ \\
                \hline

                           &  $1$  & $3.253314$ & $3.253314$ & $3.253314$ \\
                           &  $2$  & $3.253314$ & $3.152328$ & $3.152328$ \\
                           &  $3$  & $3.162691$ & $3.141827$ & $3.039048$ \\
                           &  $4$  & $3.162691$ & $3.118679$ & $3.025273$ \\
                           &  $5$  & $3.161921$ & $3.110967$ & $3.017944$ \\
    \multirow{2}{*}{$1.0$} &  $6$  & $3.161921$ & $3.103338$ & $3.013923$ \\
                           &  $7$  & $3.161909$ & $3.099324$ & $3.011405$ \\
                           &  $8$  & $3.161909$ & $3.095916$ & $3.009621$ \\
                           &  $9$  & $3.161909$ & $3.093662$ & $3.008343$ \\
                           &  $10$ & $3.161909$ & $3.091818$ & $3.007357$ \\
                           &  $11$ & $3.161909$ & $3.090436$ & $3.006590$ \\
                           &  $12$ & $3.161909$ & $3.089299$ & $3.005970$ \\
                \hline

                           &  $1$  & $5.772454$ & $5.772454$ & $5.772454$ \\
                           &  $2$  & $5.772454$ & $5.671234$ & $5.671234$ \\
                           &  $3$  & $5.679048$ & $5.658272$ & $5.553528$ \\
                           &  $4$  & $5.679048$ & $5.631669$ & $5.534333$ \\
                           &  $5$  & $5.677282$ & $5.622092$ & $5.523490$ \\
    \multirow{2}{*}{$2.0$} &  $6$  & $5.677282$ & $5.613118$ & $5.517552$ \\
                           &  $7$  & $5.677206$ & $5.608130$ & $5.513709$ \\
                           &  $8$  & $5.677206$ & $5.604026$ & $5.511012$ \\
                           &  $9$  & $5.677204$ & $5.601216$ & $5.509050$ \\
                           &  $10$ & $5.677204$ & $5.598946$ & $5.507540$ \\
                           &  $11$ & $5.677204$ & $5.597213$ & $5.506356$ \\
                           &  $12$ & $5.677204$ & $5.595791$ & $5.505399$ \\
            \end{tabular}
        \end{ruledtabular}
        \label{tab:N2}
    \end{table}

    \begin{table}
        \centering
        \caption{N = 6}
        \begin{ruledtabular}
            \begin{tabular}{c|c|ccc}
                $\omega$ & $R$ & RHF & CCD(HO) & CCD(HF) \\ \hline
                         &  $2$  & $4.864244$ & $4.864244$ & $4.864244$ \\
                         &  $3$  & $4.435740$ & \nan & $4.319901$ \\
                         &  $4$  & $4.019787$ & \nan & $3.829962$ \\
                         &  $5$  & $3.963149$ & \nan & $3.666722$ \\
  \multirow{2}{*}{$0.1$} &  $6$  & $3.870617$ & \nan & $3.597876$ \\
                         &  $7$  & $3.863135$ & \nan & $3.590388$ \\
                         &  $8$  & $3.852880$ & \nan & $3.587711$ \\
                         &  $9$  & $3.852591$ & \nan & $3.587291$ \\
                         &  $10$ & $3.852393$ & \nan & $3.587136$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $2$  & $13.640713$ & $13.640713$ & $13.640713$ \\
                         &  $3$  & $13.051620$ & $13.385987$ & $12.901520$ \\
                         &  $4$  & $12.357471$ & $13.261097$ & $12.057345$ \\
                         &  $5$  & $12.325128$ & $13.138572$ & $11.934988$ \\
  \multirow{2}{*}{$0.5$} &  $6$  & $12.271499$ & $13.084158$ & $11.864098$ \\
                         &  $7$  & $12.271375$ & $13.068399$ & $11.849762$ \\
                         &  $8$  & $12.271361$ & $13.055561$ & $11.841330$ \\
                         &  $9$  & $12.271337$ & $13.045386$ & $11.835470$ \\
                         &  $10$ & $12.271326$ & $13.037878$ & $11.831351$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $2$  & $22.219813$ & $22.219813$ & $22.219813$ \\
                         &  $3$  & $21.593198$ & $21.974675$ & $21.423811$ \\
                         &  $4$  & $20.766919$ & $21.854191$ & $20.429265$ \\
                         &  $5$  & $20.748402$ & $21.793624$ & $20.332454$ \\
  \multirow{2}{*}{$1.0$} &  $6$  & $20.720257$ & $21.750091$ & $20.274013$ \\
                         &  $7$  & $20.720132$ & $21.718843$ & $20.249849$ \\
                         &  $8$  & $20.719248$ & $21.695224$ & $20.234705$ \\
                         &  $9$  & $20.719248$ & $21.675931$ & $20.224389$ \\
                         &  $10$ & $20.719217$ & $21.661830$ & $20.21707530$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\ \hline

                         &  $2$  & $37.281425$ & $37.281425$ & $37.281425$ \\
                         &  $3$  & $36.637217$ & $37.042127$ & $36.450634$ \\
                         &  $4$  & $35.689555$ & $36.925664$ & $35.328432$ \\
                         &  $5$  & $35.681729$ & $36.864367$ & $35.250185$ \\
  \multirow{2}{*}{$2.0$} &  $6$  & $35.672333$ & $36.812895$ & $35.200308$ \\
                         &  $7$  & $35.671851$ & $36.775986$ & $35.168245$ \\
                         &  $8$  & $35.670358$ & $36.747864$ & $35.147097$ \\
                         &  $9$  & $35.670333$ & $36.725261$ & $35.131953$ \\
                         &  $10$ & $35.670144$ & $36.708362$ & $35.121033$ \\
                         &  $11$ & & & \\
                         &  $12$ & & & \\
